Protein structure representation learning has emerged as a critical area in machine learning (ML) and computational biology, with promising applications in drug discovery, protein design, and protein function prediction. Despite promising advancement, there remains a need for a robust, standardized benchmark to measure and compare the performance of various representation learning algorithms with greater granularity and relevance to downstream applications. In this work, we introduce a comprehensive and open benchmark suite for evaluating protein structure representation learning methods.

We provide several pre-training corpuses comprised of both experimental and predicted structures, offering a balanced challenge to representation learning algorithms. We also propose a set of performance metrics, including classification accuracy, retrieval performance, and transfer learning capabilities, to assess various aspects of the learned representations. These metrics enable the evaluation of the quality of the embeddings, the structural and functional relationships captured, and their usefulness in downstream tasks such as protein-protein interaction prediction and protein folding. We evaluate several state-of-the-art geometric graph neural network structural encoders, including. Our analysis reveals the strengths and weaknesses of each method, highlighting potential avenues for improvement and guiding future research in the field.

We aim to establish a common ground for the machine learning and computational biology communities to collaborate, compare, and advance protein structure representation learning research. By providing a standardized evaluation platform, we expect to accelerate the development of novel methodologies and improve our understanding of protein structures and their functions. The benchmark incorporates several engineering contributions which we believe will reduce the barrier to pre-training and working with large structure-based models.