\section{Introduction}
Proteins play central roles in cellular processes and understanding their function is...


Developments in protein structure prediction methods have led to an explosion in the availability of structural data. This has resulted in a significant gap between meaningful annotations due to the significant. 


Several deep learning methods have been developed to learn from protein structures. 


In this work we develop a large-scale framework for developing and evaluating protein structural encoders, providing several pre-training corpuses that span known foldspace and tasks that assess the ability of models to learn informative representations at different levels of structural granularity.

Previous works in protein structure representation learning have focussed on learning effective \emph{global} (i.e. graph-level) representations of protein structure, typically evaluating the methods on function or fold classification tasks. However, there has been comparatively little investigation into the ability of different methods to learn informative local (\emph{node-level}) representations. Good node-level representations are important for a variety of annotation tasks, such as binding or interaction site prediction, as well as providing conditioning signals in structure-conditioned molecule design methods. Crucially, understanding the structure-function relationship at this granular level can drive progress in protein design by revealing structural motifs that underlie desirable properties enabling them to be incorporated into designs.



Our contributions are as follows:

\begin{enumerate}
    \item 
\end{enumerate}